---
title: "MATH301 Data Modeling"
author: "Shunji & Jade"
date: "2022-10-01"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(brms)
library(ggplot2)
library(bestNormalize)
library(dplyr)
library(reclin2)
library(readr)
library(rmutil)
library(caret)
data <- read.csv(file = "insurance.csv")
```


```{r}
data[1, ]
ggplot(data, aes(x = charges)) + geom_density() + theme_bw()
chargesBN <- bestNormalize(data$charges, r = 1, k = 5)
chargesBN
data$transformed_charges <- chargesBN$x.t
ggplot(data, aes(x = transformed_charges)) + geom_density() + theme_bw()
```

```{r}
# assign 1 to male and 2 to female
data$sex <- ifelse(data$sex == "male", 1, 2)
data$age_cat <- as.factor(ifelse(data$age < 30, 1,
                          ifelse(data$age < 50, 2, 3)))
original <- data
```

```{r}
ff1 <- stats::as.formula(transformed_charges ~ 1 + bmi + smoker + region)
model1 <- stats::model.frame(ff1, data)
X1 <- data.frame(stats::model.matrix(ff1, model1))
```

```{r}
fit1 <- brms::brm(data = data,
                  family = gaussian,
                  transformed_charges ~ 1 + bmi + smoker + region,
                  iter = 5000,
                  warmup = 3000,
                  thin = 1,
                  chains = 1,
                  seed = 1)
```

```{r}
post_fit1 <- brms::posterior_samples(x = fit1)
post_fit1[1:3, ]
```

```{r}
# bayesplot::mcmc_trace(x = fit1, 
#                       pars = c("b_Intercept", "b_bmi",
#                              "b_smokeryes", "b_regionnorthwest",
#                              "b_regionsoutheast",
#                              "b_regionsouthwest", "sigma"))
# bayesplot::mcmc_acf(x = fit1, 
#                     pars = c("b_Intercept", "b_bmi",
#                              "b_smokeryes", "b_regionnorthwest",
#                              "b_regionsoutheast",
#                              "b_regionsouthwest", "sigma"))

synthesize1_func <- function(X, post_draws, index, n, seed){
  set.seed(seed)
  mean_Y <- as.matrix(X) %*%
  t(data.matrix(post_draws[index, c("b_Intercept", "b_bmi",
                                   "b_smokeryes", "b_regionnorthwest",
                                   "b_regionsoutheast",
                                   "b_regionsouthwest")]))
  synthetic_Y <- stats::rnorm(n, mean_Y, post_draws[index, "sigma"])
  data.frame(X, synthetic_Y)
}

n <- nrow(data)
synthetic1 <- synthesize1_func(X = X1,
                              post_draws = post_fit1,
                              index = 1,
                              n = nrow(X1),
                              seed = 2)
names(synthetic1) <- c("Intercept", "bmi",
                       "smokeryes", "regionnorthwest",
                       "regionsoutheast",
                       "regionsouthwest", "transformed_charges")
```

```{r}
df1 <- data.frame(confidential = data$transformed_charges,
                 synthetic = synthetic1$transformed_charges)
df_long1 <- reshape2::melt(df1)

ggplot2::ggplot(data = df_long1, aes(value, colour = variable, linetype = variable)) +
  geom_density() +
  scale_colour_manual(values = c("#E69F00", "#999999"),
                      guide = guide_legend(override.aes = list(
                        linetype = c(1, 2)))) +
  scale_linetype_manual(values = c(1, 2), guide = FALSE) +
  ggtitle("Density plots of transformed_charges") +
  xlab("transformed_charges") +
  theme_bw(base_size = 15, base_family = "") +
  theme(legend.title = element_blank())
```

```{r}
reversed_charges <- predict(chargesBN,
                            newdata = synthetic1$transformed_charges, inverse = TRUE)
df2 <- data.frame(confidential = data$charges, 
                 synthetic = reversed_charges)
df_long2 <- reshape2::melt(df2)

ggplot2::ggplot(data = df_long2, aes(value, colour = variable, linetype = variable)) +
  geom_density() + 
  scale_colour_manual(values = c("#E69F00", "#999999"),
                      guide = guide_legend(override.aes = list(
                        linetype = c(1, 2)))) + 
  scale_linetype_manual(values = c(1, 2), guide = FALSE) + 
  ggtitle("Density plots of transformed_charges") + 
  xlab("transformed_charges") + 
  theme_bw(base_size = 15, base_family = "") +
  theme(legend.title = element_blank())
```

```{r}
data$transformed_charges_synthetic <- synthetic1$transformed_charges
ff2 <- stats::as.formula((sex - 1) ~ 1 + bmi + 
                           smoker + region + transformed_charges_synthetic)
model2 <- stats::model.frame(ff2, data)
X2 <- data.frame(stats::model.matrix(ff2, model2))
```

```{r}
fit2 <- brms::brm(data = data,
                          family = bernoulli(link = "logit"),
                          (sex - 1) ~ 1 + bmi + smoker + region + transformed_charges,
                          iter = 5000,
                          warmup = 3000,
                          thin = 1,
                          chains = 1,
                          seed = 3)
```

```{r}
post_fit2 <- brms::posterior_samples(x = fit2)
post_fit2[1:3, ]
```

```{r}
# bayesplot::mcmc_trace(x = fit2, 
#                       pars = c("b_Intercept", "b_bmi",
#                                "b_smokeryes", "b_regionnorthwest",
#                                "b_regionsoutheast", "b_regionsouthwest",
#                                "b_transformed_charges"))
# bayesplot::mcmc_acf(x = fit2, 
#                     pars = c("b_Intercept", "b_bmi",
#                              "b_smokeryes", "b_regionnorthwest",
#                              "b_regionsoutheast", "b_regionsouthwest",
#                              "b_transformed_charges"))

synthesize2_func <- function(X, post_draws, index, n, seed){
  set.seed(seed)
  log_p <- as.matrix(X) %*%
  t(data.matrix(post_draws[index, c("b_Intercept", "b_bmi",
                                     "b_smokeryes", "b_regionnorthwest",
                                     "b_regionsoutheast", "b_regionsouthwest",
                                     "b_transformed_charges")]))
  p <- exp(log_p) / (1 + exp(log_p))
  synthetic_Y <- stats::rbinom(n, size = 1, prob = p) + 1
  data.frame(X, synthetic_Y)
}

n <- nrow(data)
synthetic2 <- synthesize2_func(X = X2,
                              post_draws = post_fit2,
                              index = 1,
                              n = nrow(X2),
                              seed = 4)
names(synthetic2) <- c("Intercept", "bmi",
                       "smokeryes", "regionnorthwest",
                       "regionsoutheast", "regionsouthwest",
                       "transformed_charges", "sex")
```

```{r}
df3 <- data.frame(confidential = data$sex, 
                 synthetic = synthetic2$sex)
df_long3 <- reshape2::melt(df3)

ggplot2::ggplot(data = df_long3, aes(x = value, fill = variable)) +
  geom_histogram(binwidth = 0.5, position = position_dodge()) +  
  scale_fill_manual(values = c("#E69F00", "#999999")) + 
  ggtitle("Confidential Sex vs Synthetic Sex") + 
  xlab("Sex") + 
  theme_bw(base_size = 15, base_family = "") +
  theme(legend.title = element_blank()) 
```

```{r}
data$sex_synthetic <- synthetic2$sex
ff3 <- stats::as.formula(age_cat ~ 1 + bmi + 
                           smoker + region + 
                           transformed_charges_synthetic + sex_synthetic)
model3 <- stats::model.frame(ff3, data)
X3 <- data.frame(stats::model.matrix(ff3, model3))
```

```{r}
fit3 <- brms::brm(data = data,
                    family = categorical(link = "logit"),
                    age_cat ~ 1 + bmi + 
                           smoker + region + 
                           transformed_charges + sex,
                    iter = 5000,
                    warmup = 3000,
                    thin = 1,
                    chains = 1,
                    seed = 5)
```

```{r}
post3 <- brms::posterior_samples(x = fit3)
post3[1:3, ]
```

```{r}
synthesize3_func <- function(X, post_draws, index, n, C, seed){
  set.seed(seed)
  log_p_allC <- matrix(NA, nrow = n, ncol = C)
  for (c in 2:C){
    name_Intercept_c <- paste0("b_mu", c, "_Intercept")
    name_bmi_c <- paste0("b_mu", c, "_bmi")
    name_smokeryes_c <- paste0("b_mu", c, "_smokeryes")
    name_regionnorthwest_c <- paste0("b_mu", c, "_regionnorthwest")
    name_regionsoutheast_c <- paste0("b_mu", c, "_regionsoutheast")
    name_regionsouthwest_c <- paste0("b_mu", c, "_regionsouthwest")
    name_transformed_charges_c <- paste0("b_mu", c, "_transformed_charges")
    name_sex_c <- paste0("b_mu", c, "_sex")
    log_p_c <- as.matrix(X) %*% 
      t(post_draws[index, 
                   c(name_Intercept_c, name_bmi_c,
                     name_smokeryes_c, name_regionnorthwest_c,
                     name_regionsoutheast_c, name_regionsouthwest_c,
                     name_transformed_charges_c, name_sex_c)])
    log_p_allC[, c] <- log_p_c
  }
  log_p_allC[, 1] <- rep(0, n)
  p_allC <- exp(log_p_allC) / (1 + exp(log_p_allC))
  
  synthetic_Y <- rep(NA, n)
  for (i in 1:n){
    synthetic_Y[i] <- which(stats::rmultinom(n = 1, size = 1,
                                            prob = p_allC[i, ]) == 1)
  }
  data.frame(X, synthetic_Y)
}

synthetic3 <- synthesize3_func(X = X3,
                              post_draws = post3,
                              index = 1,
                              n = nrow(X3),
                              C = 3,
                              seed = 6)
names(synthetic3) <- c("Intercept", "bmi", "smokeryes", 
                       "northwest", "southeast", "southwest",
                       "transformed_charges", "sex", "age_cat")
```

```{r}
df4 <- data.frame(confidential = as.numeric(data$age_cat),
                 synthetic = as.numeric(synthetic3$age_cat))
df_long4 <- reshape2::melt(df4)

ggplot2::ggplot(data = df_long4, aes(x = value, fill = variable)) +
  geom_histogram(binwidth = 0.5, position = position_dodge()) +  
  scale_fill_manual(values = c("#E69F00", "#999999")) + 
  ggtitle("Confidential age vs synthetic age") + 
  xlab("age groups") + 
  theme_bw(base_size = 15, base_family = "") +
  theme(legend.title = element_blank())

data$age_cat_synthetic <- synthetic3$age_cat
```

```{r}
org <- original %>% dplyr::select("sex", "bmi", "children", 
                           "smoker", "region", "charges", "age_cat")
data$charges <- predict(chargesBN, newdata = data$transformed_charges_synthetic,
                        inverse = TRUE)
syn <- data %>% dplyr::select("sex_synthetic", "bmi", "children",
                       "smoker", "region", "charges", "age_cat_synthetic")
syn <- syn %>% rename(sex = sex_synthetic, age_cat = age_cat_synthetic)
syn$age_cat <- factor(syn$age_cat)
```

\subsection{Global utility check: eCDF}

```{r}
merged_data <- rbind(org, syn)
merged_data$S <- c(rep(0, n), rep(1, n))

ecdf_orig0 <- stats::ecdf(org$charges)
ecdf_syn0 <- stats::ecdf(syn$charges)

percentile_orig0 <- ecdf_orig0(merged_data$charges)
percentile_syn0 <- ecdf_syn0(merged_data$charges)

ecdf_diff0 <- percentile_orig0 - percentile_syn0
Um0 <- max(abs(ecdf_diff0))
Um0
Ua0 <- mean(ecdf_diff0^2)
Ua0

ecdf_orig1 <- stats::ecdf(org$sex)
ecdf_syn1 <- stats::ecdf(syn$sex)

percentile_orig1 <- ecdf_orig1(merged_data$sex)
percentile_syn1 <- ecdf_syn1(merged_data$sex)

ecdf_diff1 <- percentile_orig1 - percentile_syn1
Um1 <- max(abs(ecdf_diff1))
Um1
Ua1 <- mean(ecdf_diff1^2)
Ua1

ecdf_orig2 <- stats::ecdf(org$age_cat)
ecdf_syn2 <- stats::ecdf(syn$age_cat)

percentile_orig2 <- ecdf_orig2(merged_data$age_cat)
percentile_syn2 <- ecdf_syn2(merged_data$age_cat)

ecdf_diff2 <- percentile_orig2 - percentile_syn2
Um2 <- max(abs(ecdf_diff2))
Um2
Ua2 <- mean(ecdf_diff2^2)
Ua2
```

\subsection{Global utility check: pMSE}

```{r}
log_reg <- stats::glm(formula = S ~ (as.factor(sex) + bmi + as.factor(children) +
                                       smoker + region + charges + as.factor(age_cat))^2,
                      family = "binomial",
                      data = merged_data)

pred <- stats::predict(log_reg,
                       data = merged_data)
probs <- exp(pred) / (1 + exp(pred))

pMSE <- 1 / (2 * n) * sum((probs - 1 / 2)^2)
pMSE
```


\subsection{Inference for average charges}

```{r}
n <- nrow(org)
m <- 20
synthetic_m_partial <- vector("list", m)
for (l in 1:m) {
  synthetic_one_partial <- synthesize3_func(X = X3,
                                            post_draws = post3,
                                            index = l,
                                            n = n,
                                            C = 3,
                                            seed = m + l)
  names(synthetic_one_partial) <- c("Intercept", "bmi", "smokeryes", 
                                     "northwest", "southeast", "southwest",
                                     "transformed_charges", "sex", "age_cat")
  synthetic_one_partial$charges <- predict(chargesBN, newdata = 
                                             synthetic_one_partial$transformed_charges,
                                           inverse = TRUE)
  synthetic_m_partial[[l]] <- synthetic_one_partial
}

q <- rep(NA, m)
v <- rep(NA, m)
for (l in 1:m){
  synthetic_one_partial <- synthetic_m_partial[[l]]
  q[l] <- mean(synthetic_one_partial$charges)
  v[l] <- var(synthetic_one_partial$charges)/n
}

q_bar_m <- mean(q)
b_m <- var(q)
v_bar_m <- mean(v)

T_p <- b_m / m + v_bar_m
v_p <- (m - 1) * (1 + v_bar_m / (b_m / m))^2

q_bar_m
t_score_syn <- qt(p = 0.975, df = v_p)
c(q_bar_m - t_score_syn * sqrt(T_p), 
  q_bar_m + t_score_syn * sqrt(T_p))

mean_con <- mean(org$charges)
sd_con <- sd(org$charges)
t_score_con <- qt(p = 0.975, df = n - 1)
mean_con
c(mean_con - t_score_con * sd_con / sqrt(n), 
  mean_con + t_score_con * sd_con / sqrt(n))
```

```{r}

ggplot(data, aes(x = log(syn$charges))) + geom_density()

ComputeBeta1 <- function(m, syndata, index){

Beta1_q <- rep(NA, m)
Beta1_v <- rep(NA, m)

for (l in 1:m){
  syndata_l <- syndata[[l]]
  syndata_l_lm <- stats::lm(formula = log(charges) ~ 1 + bmi + as.factor(smokeryes) +
                              as.factor(northwest) + as.factor(southeast) +
                              as.factor(southwest) + as.factor(age_cat) + 
                              as.factor(sex), data = syndata_l)
  coef_output <- coef(summary(syndata_l_lm))
  Beta1_q[l] <- coef_output[index, 1]
  Beta1_v[l] <- coef_output[index, 2]^2
}

Beta1_q_bar_m <- mean(Beta1_q)
Beta1_b_m <- var(Beta1_q)
Beta1_v_bar_m <- mean(Beta1_v)

Beta1_T_p <- Beta1_b_m / m + Beta1_v_bar_m

Beta1_v_p <- (m - 1) * (1 + Beta1_v_bar_m / (Beta1_b_m / m))^2


Beta1_t_score_syn <- qt(p = 0.975, df = Beta1_v_p)
print(c(Beta1_q_bar_m, Beta1_q_bar_m - Beta1_t_score_syn * sqrt(Beta1_T_p),
        Beta1_q_bar_m + Beta1_t_score_syn * sqrt(Beta1_T_p)))
}

for (i in 2:9) {
  ComputeBeta1(m = m, syndata = synthetic_m_partial, index = i)
}


confidata_lm <- stats::lm(formula = log(charges) ~ 1 + bmi + smoker + region + age_cat + sex, data = org)
coef(summary(confidata_lm))
confint(confidata_lm)
```

\subsection{Interval overlap utility measure definition 2}

```{r}
CalculateIntervalOverlap_v2 <- function(confi_interval, syn_interval){
  
  L_c <- confi_interval[1]
  U_c <- confi_interval[2]
  L_s <- syn_interval[1]
  U_s <- syn_interval[2]
  
  overlap <- 1 / 2 * ((min(U_c, U_s) - max(L_c, L_s)) / (U_c - L_c) + 
                        (min(U_c, U_s) - max(L_c, L_s)) / (U_s - L_s))
  
  return(overlap) 
}

IO1 <- CalculateIntervalOverlap_v2(c(12908.45, 14290.87), 
                                   c(12620.95, 13919.89))
IO1

IO2 <- CalculateIntervalOverlap_v2(c(0.0094, 0.0185), 
                                   c(0.0195, 0.0306))
IO2

IO3 <- CalculateIntervalOverlap_v2(c(1.4891, 1.6201), 
                                   c(1.3576, 1.5200))
IO3

IO4 <- CalculateIntervalOverlap_v2(c(-0.1294, 0.0214), 
                                   c(-0.1131, 0.0728))
IO4

IO5 <- CalculateIntervalOverlap_v2(c(-0.2372, -0.0855), 
                                   c(-0.3110, -0.1232))
IO5

IO6 <- CalculateIntervalOverlap_v2(c(-0.1968, -0.0454), 
                                   c(-0.2349, -0.0473))
IO6

IO7 <- CalculateIntervalOverlap_v2(c(0.6153, 0.7409), 
                                   c(0.2770, 0.4329))
IO7

IO8 <- CalculateIntervalOverlap_v2(c(1.1190, 1.2558), 
                                   c(0.6229, 0.7985))
IO8

IO9 <- CalculateIntervalOverlap_v2(c(0.0212, 0.1267), 
                                   c(0.0753, 0.2073))
IO9
```

\subsection{Risk evaluation: matched based}

```{r}
n <- dim(org)[1]
syn <- syn[, names(org)]
con <- org

CalculateKeyQuantities_cat <- function(condata, syndata, 
                                   known.vars, syn.vars, n){
  condata <- condata
  syndata <- syndata
  n <- n

  c_vector <- rep(NA, n)
  T_vector <- rep(NA, n)

  for (i in 1:n){
    match <- (eval(parse(text=paste("condata$",syn.vars,
                                    "[i]==syndata$",syn.vars,
                                    sep="",collapse="&")))&
                  eval(parse(text=paste("condata$",known.vars,
                                        "[i]==syndata$",
                                        known.vars,sep="",
                                        collapse="&"))))
    match.prob <- ifelse(match, 1/sum(match), 0)
    
    if (max(match.prob) > 0){
      c_vector[i] <- length(match.prob[match.prob 
                                       == max(match.prob)])
    }
    else
      c_vector[i] <- 0
      T_vector[i] <- is.element(i, rownames(condata)
                                [match.prob == max(match.prob)])
  }
  
  K_vector <- (c_vector * T_vector == 1)
  F_vector <- (c_vector * (1 - T_vector) == 1)
  s <- length(c_vector[c_vector == 1 & is.na(c_vector) == FALSE])
  
  res_r <- list(c_vector = c_vector,
                T_vector = T_vector,
                K_vector = K_vector,
                F_vector = F_vector,
                s = s
  )
  return(res_r)
}

KeyQuantities <- CalculateKeyQuantities_cat(condata = con, 
                                                syndata = syn, 
                                                known.vars = c("children", 
                                                               "smoker", 
                                                               "region"),
                                                syn.vars = c("sex", 
                                                             "age_cat"), 
                                                n = n)

IdentificationRiskCal <- function(c_vector, T_vector, 
                                  K_vector, F_vector, 
                                  s, N){
  
  nonzero_c_index <- which(c_vector > 0)

  exp_match_risk <- sum(1/c_vector[nonzero_c_index] * 
                          T_vector[nonzero_c_index])
  true_match_rate <- sum(na.omit(K_vector))/N
  false_match_rate <- sum(na.omit(F_vector))/s

  res_r <- list(exp_match_risk = exp_match_risk,
                true_match_rate = true_match_rate,
                false_match_rate = false_match_rate
  )
  return(res_r)
}

res <- IdentificationRiskCal(c_vector = KeyQuantities[["c_vector"]], 
                                 T_vector = KeyQuantities[["T_vector"]],
                                 K_vector = KeyQuantities[["K_vector"]], 
                                 F_vector = KeyQuantities[["F_vector"]],
                                 s = KeyQuantities[["s"]], 
                                 N = n)

res[["exp_match_risk"]]
res[["true_match_rate"]]
res[["false_match_rate"]]
KeyQuantities[["s"]]

KeyQuantities <- CalculateKeyQuantities_cat(condata = con, 
                                                syndata = con, 
                                                known.vars = c("children", 
                                                               "smoker", 
                                                               "region"),
                                                syn.vars = c("sex", 
                                                             "age_cat"), 
                                                n = n)

res <- IdentificationRiskCal(c_vector = KeyQuantities[["c_vector"]], 
                                 T_vector = KeyQuantities[["T_vector"]],
                                 K_vector = KeyQuantities[["K_vector"]], 
                                 F_vector = KeyQuantities[["F_vector"]],
                                 s = KeyQuantities[["s"]], 
                                 N = n)

res[["exp_match_risk"]]
res[["true_match_rate"]]
res[["false_match_rate"]]
KeyQuantities[["s"]]
```

```{r}
CalculateKeyQuantities_cont <- function(condata, syndata, 
                                   known.vars, syn.vars, 
                                   n, r){
  condata <- condata
  syndata <- syndata
  n <- n

  c_vector <- rep(NA, n)
  T_vector <- rep(NA, n)

  for (i in 1:n){
    radius <- r*eval(parse(text=paste("condata$",syn.vars,"[i]")))
    match <- (eval(parse(text=paste("syndata$",syn.vars,
                                    "<=condata$",syn.vars,
                                    "[i]+",radius,sep="",
                                    collapse="&")))&
                eval(parse(text=paste("syndata$",syn.vars,
                                    ">=condata$",syn.vars,
                                    "[i]-",radius,sep="",
                                    collapse="&")))&
                eval(parse(text=paste("condata$",known.vars,
                                        "[i]==syndata$",
                                        known.vars,sep="",
                                        collapse="&"))))
    match.prob <- ifelse(match, 1/sum(match), 0)
    
    if (max(match.prob) > 0){
      c_vector[i] <- length(match.prob[match.prob 
                                       == max(match.prob)])
    }
    else
      c_vector[i] <- 0
      T_vector[i] <- is.element(i, rownames(condata)
                                [match.prob == max(match.prob)])
  }
  
  K_vector <- (c_vector * T_vector == 1)
  F_vector <- (c_vector * (1 - T_vector) == 1)
  s <- length(c_vector[c_vector == 1 & is.na(c_vector) == FALSE])
  
  res_r <- list(c_vector = c_vector,
                T_vector = T_vector,
                K_vector = K_vector,
                F_vector = F_vector,
                s = s
  )
  return(res_r)
}

KeyQuantities <- CalculateKeyQuantities_cont(condata = con, 
                                              syndata = syn, 
                                              known.vars = c("children", 
                                                             "smoker",
                                                             "region"), 
                                              syn.vars = c("charges"), 
                                              n = n, 
                                              r = 0.2)

res <- IdentificationRiskCal(c_vector = KeyQuantities[["c_vector"]], 
                              T_vector = KeyQuantities[["T_vector"]], 
                              K_vector = KeyQuantities[["K_vector"]],
                              F_vector = KeyQuantities[["F_vector"]], 
                              s = KeyQuantities[["s"]], 
                              N = n)

res[["exp_match_risk"]]
res[["true_match_rate"]]
res[["false_match_rate"]]
KeyQuantities[["s"]]

KeyQuantities <- CalculateKeyQuantities_cont(condata = con, 
                                              syndata = con, 
                                              known.vars = c("children", 
                                                             "smoker",
                                                             "region"), 
                                              syn.vars = c("charges"), 
                                              n = n, 
                                              r = 0.2)

res <- IdentificationRiskCal(c_vector = KeyQuantities[["c_vector"]], 
                              T_vector = KeyQuantities[["T_vector"]], 
                              K_vector = KeyQuantities[["K_vector"]],
                              F_vector = KeyQuantities[["F_vector"]], 
                              s = KeyQuantities[["s"]], 
                              N = n)

res[["exp_match_risk"]]
res[["true_match_rate"]]
res[["false_match_rate"]]
KeyQuantities[["s"]]
```

\subsection{Risk evaluation: record linkage}

```{r}
con$id <- 1:n
syn$id <- 1:n

pairs <- reclin2::pair_blocking(syn, con, 
                               c("children", "smoker", "region"))

pairs_keys <- reclin2::compare_pairs(pairs, 
                                    on = c("sex", "age_cat", "charges"))

m <- reclin2::problink_em(formula = ~ sex + age_cat + charges, data = pairs_keys)
pairs_keys_pRL <- predict(pairs = pairs_keys, 
                           object = m, 
                           type = "weights")
pairs_keys_pRL <- reclin2::select_greedy(pairs_keys_pRL, 
                                          "weights", 
                                          var = "greedy", 
                                          threshold = 0)
pairs_keys_pRL$true <- pairs_keys_pRL$.x == pairs_keys_pRL$.y
table(as.data.frame(pairs_keys_pRL)[c("true", "greedy")])

pairs <- reclin2::pair_blocking(con, con, 
                               c("children", "smoker", "region"))

pairs_keys <- reclin2::compare_pairs(pairs, 
                                    on = c("sex", "age_cat", "charges"))

m <- reclin2::problink_em(formula = ~ sex + age_cat + charges, data = pairs_keys)
pairs_keys_pRL <- predict(pairs = pairs_keys, 
                           object = m, 
                           type = "weights")
pairs_keys_pRL <- reclin2::select_greedy(pairs_keys_pRL, 
                                          "weights", 
                                          var = "greedy", 
                                          threshold = 0)
pairs_keys_pRL$true <- pairs_keys_pRL$.x == pairs_keys_pRL$.y
table(as.data.frame(pairs_keys_pRL)[c("true", "greedy")])
```

\subsection{Risk evaluation: CAP}

```{r}
CalculateIndividualCAP <- function(condata_i, syndata, 
                                   key.vars, target.vars){
  condata_i <- condata_i
  syndata <- syndata
  m <- nrow(syndata)
  
  match_key <- eval(parse(text=paste("condata_i$",key.vars,
                                     "==syndata$",
                                     key.vars,sep="",
                                     collapse="&")))
  
  match_key_target <- (eval(parse(text=paste("condata_i$",key.vars,
                                             "==syndata$",key.vars,
                                             sep="",collapse="&")))&
                         eval(parse(text=paste("condata_i$",target.vars,
                                               "==syndata$",target.vars,
                                               sep="",collapse="&"))))
  
  if (sum(match_key) > 0)
    CAP_i <- sum(match_key_target) / sum(match_key)
  else
    CAP_i <- 0
  
  return(CAP_i)
}
```

```{r}
CAP_syn_all <- rep(NA, n)
for (i in 1:n){
  CAP_syn_all[i] <- CalculateIndividualCAP(condata_i = con[i, ], 
                                           syndata = syn,
                                           key.vars = c("children", 
                                                        "smoker", 
                                                        "region"),
                                           target.vars = c("sex"))
}
mean(CAP_syn_all)
```

```{r}
CAP_syn_all <- rep(NA, n)
for (i in 1:n){
  CAP_syn_all[i] <- CalculateIndividualCAP(condata_i = con[i, ], 
                                           syndata = con,
                                           key.vars = c("children", 
                                                        "smoker", 
                                                        "region"),
                                           target.vars = c("sex"))
}
mean(CAP_syn_all)
```

```{r}
CAP_syn_all <- rep(NA, n)
for (i in 1:n){
  CAP_syn_all[i] <- CalculateIndividualCAP(condata_i = con[i, ], 
                                           syndata = syn,
                                           key.vars = c("children", 
                                                        "smoker", 
                                                        "region"),
                                           target.vars = c("age_cat"))
}
mean(CAP_syn_all)
```

```{r}
CAP_syn_all <- rep(NA, n)
for (i in 1:n){
  CAP_syn_all[i] <- CalculateIndividualCAP(condata_i = con[i, ], 
                                           syndata = con,
                                           key.vars = c("children", 
                                                        "smoker", 
                                                        "region"),
                                           target.vars = c("age_cat"))
}
mean(CAP_syn_all)
```

```{r}
CalculateIndividualCAP <- function(condata_i, syndata, 
                                   key.vars, target.vars, r){
  condata_i <- condata_i
  syndata <- syndata
  m <- nrow(syndata)
  
  match_key <- eval(parse(text=paste("condata_i$",key.vars,
                                     "==syndata$",
                                     key.vars,sep="",
                                     collapse="&")))
  radius <- r*eval(parse(text=paste("condata_i$",target.vars)))
  match_key_target <- (eval(parse(text=paste("syndata$",target.vars,
                                            "<=condata_i$",target.vars,
                                            "+",radius,sep="",
                                            collapse="&")))&
                        eval(parse(text=paste("syndata$",target.vars,
                                            ">=condata_i$",target.vars,
                                            "-",radius,sep="",
                                            collapse="&")))&
                        eval(parse(text=paste("condata_i$",key.vars,
                                                "==syndata$",
                                                key.vars,sep="",
                                                collapse="&"))))
  
  if (sum(match_key) > 0)
    CAP_i <- sum(match_key_target) / sum(match_key)
  else
    CAP_i <- 0
  
  return(CAP_i)
}
```


```{r}
CAP_syn_all <- rep(NA, n)
for (i in 1:n){
  CAP_syn_all[i] <- CalculateIndividualCAP(condata_i = con[i, ], 
                                           syndata = syn,
                                           key.vars = c("children", 
                                                        "smoker", 
                                                        "region"),
                                           target.vars = c("charges"),
                                           r = 0.2)
}
mean(CAP_syn_all)
```

```{r}
CAP_syn_all <- rep(NA, n)
for (i in 1:n){
  CAP_syn_all[i] <- CalculateIndividualCAP(condata_i = con[i, ], 
                                           syndata = con,
                                           key.vars = c("children", 
                                                        "smoker", 
                                                        "region"),
                                           target.vars = c("charges"),
                                           r = 0.2)
}
mean(CAP_syn_all)
```

\subsection{Risk evaluation: classification-based}

```{r}
set.seed(301)
fit.knn_syn <- caret::train(charges ~ as.factor(sex) + bmi + as.factor(children) + 
                              as.factor(smoker) + as.factor(region) + as.factor(age_cat),
                            data=syn,
                            preProcess=c("center", "scale"),
                            method="knn",
                            tuneGrid = data.frame(k=c(10)),
                            trControl=trainControl(method="none"),
                            metric="RMSE",
                            na.action=na.omit)

pred_syn <- predict(fit.knn_syn, newdata=subset(con, select=c(sex, bmi, children,
                                                              smoker, region, age_cat)))

fit.knn_con <- caret::train(charges ~ as.factor(sex) + bmi + as.factor(children) + 
                              as.factor(smoker) + as.factor(region) + as.factor(age_cat),
                            data=con,
                            preProcess=c("center", "scale"),
                            method="knn",
                            tuneGrid = data.frame(k=c(10)),
                            trControl=trainControl(method="none"),
                            metric="RMSE",
                            na.action=na.omit)

pred_con <- predict(fit.knn_con, newdata=subset(con, select=c(sex, bmi, children,
                                                              smoker, region, age_cat)))

kNN_MSE_syn <- mean((con$charges - 
                          pred_syn)^2)
kNN_MSE_syn

kNN_MSE_con <- mean((con$charges - 
                           pred_con)^2)
kNN_MSE_con

relative_error_syn <- (abs(con$charges - 
                             pred_syn)/con$charges)
relative_error_con <- (abs(con$charges - 
                             pred_con)/con$charges)
mean(relative_error_con > relative_error_syn)
```

```{r}
set.seed(301)
fit.knn_syn <- caret::train(as.factor(sex) ~ charges + bmi + as.factor(children) + 
                              as.factor(smoker) + as.factor(region) + as.factor(age_cat),
                            data=syn,
                            preProcess=c("center", "scale"),
                            method="knn",
                            tuneGrid = data.frame(k=c(10)),
                            trControl=trainControl(method="none"),
                            metric="Accuracy",
                            na.action=na.omit)

pred_syn <- predict(fit.knn_syn, newdata=subset(con, select=c(charges, bmi, children,
                                                              smoker, region, age_cat)))

fit.knn_con <- caret::train(as.factor(sex) ~ charges + bmi + as.factor(children) + 
                              as.factor(smoker) + as.factor(region) + as.factor(age_cat),
                            data=con,
                            preProcess=c("center", "scale"),
                            method="knn",
                            tuneGrid = data.frame(k=c(10)),
                            trControl=trainControl(method="none"),
                            metric="Accuracy",
                            na.action=na.omit)

pred_con <- predict(fit.knn_con, newdata=subset(con, select=c(charges, bmi, children,
                                                              smoker, region, age_cat)))

kNN_error_syn <- mean(pred_syn != con$sex)
kNN_error_syn
kNN_error_con <- mean(pred_con != con$sex)
kNN_error_con

relative_error_syn <- (pred_syn != con$sex)
relative_error_con <- (pred_con != con$sex)
mean(relative_error_con != relative_error_syn)
```

```{r}
set.seed(302)
fit.knn_syn <- caret::train(as.factor(age_cat) ~ charges + bmi + as.factor(children) + 
                              as.factor(smoker) + as.factor(region) + as.factor(sex),
                            data=syn,
                            preProcess=c("center", "scale"),
                            method="knn",
                            tuneGrid = data.frame(k=c(10)),
                            trControl=trainControl(method="none"),
                            metric="Accuracy",
                            na.action=na.omit)

pred_syn <- predict(fit.knn_syn, newdata=subset(con, select=c(charges, bmi, children,
                                                              smoker, region, sex)))

fit.knn_con <- caret::train(as.factor(age_cat) ~ charges + bmi + as.factor(children) + 
                              as.factor(smoker) + as.factor(region) + as.factor(sex),
                            data=con,
                            preProcess=c("center", "scale"),
                            method="knn",
                            tuneGrid = data.frame(k=c(10)),
                            trControl=trainControl(method="none"),
                            metric="Accuracy",
                            na.action=na.omit)

pred_con <- predict(fit.knn_con, newdata=subset(con, select=c(charges, bmi, children,
                                                              smoker, region, sex)))

kNN_error_syn <- mean(pred_syn != con$age_cat)
kNN_error_syn

kNN_error_con <- mean(pred_con != con$age_cat)
kNN_error_con

relative_error_syn <- (pred_syn != con$age_cat)
relative_error_con <- (pred_con != con$age_cat)
mean(relative_error_con != relative_error_syn)
```


\subsection{Differential Privacy}

```{r}
set.seed(301)
epsilon1 <- 0.1
m <- 2
epsilon_new1 <- epsilon1 / m
charges_average <- mean(con$charges)
Delta_f_average_charges <- 100000 / n
rlaplace(1, charges_average, Delta_f_average_charges/epsilon_new1)
mean(con$charges)

epsilon2 <- 1000
epsilon_new2 <- epsilon2 / m
charges_median <- median(con$charges)
rlaplace(1, charges_median, 100000/epsilon_new2)
median(con$charges)
```

```{r}
set.seed(301)
charges_male_average <- mean(subset(con, sex == 1, select = charges)$charges)
charges_female_average <- mean(subset(con, sex == 2, select = charges)$charges)

charges_male_average
rlaplace(1, charges_male_average, Delta_f_average_charges/epsilon1)

charges_female_average
rlaplace(1, charges_female_average, Delta_f_average_charges/epsilon1)
```

```{r}
set.seed(301)
charges_age1_average <- mean(subset(con, age_cat == 1)$charges)
charges_age2_average <- mean(subset(con, age_cat == 2)$charges)
charges_age3_average <- mean(subset(con, age_cat == 3)$charges)

charges_age1_average
rlaplace(1, charges_age1_average, Delta_f_average_charges/epsilon1)

charges_age2_average
rlaplace(1, charges_age2_average, Delta_f_average_charges/epsilon1)

charges_age3_average
rlaplace(1, charges_age3_average, Delta_f_average_charges/epsilon1)
```

```{r}
set.seed(301)
epsilon4 <- 0.1
n_male <- nrow(subset(con, sex == 1))
n_male
n_male_df <- round(rlaplace(1, n_male, 1 / epsilon4))
n_male_df

n_female <- nrow(subset(con, sex == 2))
n_female
nrow(con) - n_male_df
```


```{r}
set.seed(301)
epsilon3 <- 0.1
c <- 3
epsilon_new3 <- epsilon3 / (c-1)
n_age1 <- nrow(subset(con, age_cat == 1))
n_age1
n_age1_df <- round(rlaplace(1, n_age1, 2 / epsilon_new3))
n_age1_df

n_age2 <- nrow(subset(con, age_cat == 2))
n_age2
n_age2_df <- round(rlaplace(1, n_age2, 2 / epsilon_new3))
n_age2_df

n_age3 <- nrow(subset(con, age_cat == 3))
n_age3
nrow(con) - n_age1_df - n_age2_df
```


